---
title: "Analysis // #dontretirekid trends"
author: "Phil Walker"
output:
  html_document:
    df_print: paged
    code_folding: hide
    toc: true
    toc_float: true
    theme: spacelab
    includes:
      after_body: footer.html
date: "`r format(Sys.time(), '%d %B, %Y')`"
editor_options: 
  chunk_output_type: console
---

```{css, echo=FALSE}
body .main-container {
  max-width: 100% !important;
  width: 100% !important;
    }
body {
  max-width: 100% !important;
    }
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rtweet)
library(tidyverse)
```

# Overview
The hashtag "#dontretirekid" was part of the [Aspen Institute's media program](https://www.aspenprojectplay.org/dont-retire-kid) as part of the larger Project Play initiative to help promote youth sports.

We would like to be able to capture all of the tweets related to this hashtag to better understand the breadth of the expoure. Ideally, this data could then be used to assess how effective it was, or what areas it resonated with 

Below is an example of the ads that helped to spread this message out to sport consumers. 

<!-- <iframe width="560" height="315" src="https://www.youtube.com/embed/TInFe337gZQ" frameborder="0" allowfullscreen></iframe> -->

<div align="center">
   <iframe width="560" height="315" src="https://www.youtube.com/embed/TInFe337gZQ" frameborder="0" allowfullscreen>
   </iframe>
</div>

These ads are mean

# Gather Data

## Twitter

Starting with all tweets from the Aspen Institute timeline
```{r}

tl_AspendIn <- 
  get_timeline("AspenInstSports", n = 5200) %>% 
  select(status_id, reply_to_status_id, created_at, screen_name, reply_to_screen_name, mentions_screen_name,
         text, source, hashtags, urls_expanded_url, media_url,
         geo_coords, country, location,
         account_created_at, followers_count, friends_count)

tl_AspendIn %>% 
  select(hashtags) %>% 
  unnest(cols = c(hashtags)) %>% 
  count(hashtags, sort = TRUE) %>% 
  DT::datatable()


dontRetire_AIS <- 
  tl_AspendIn %>% 
  filter(str_detect(text, regex("#dontretirekid", ignore_case = TRUE)))

FirstDontRetire <- min(dontRetire_AIS$created_at)
LastDontRetire <- max(dontRetire_AIS$created_at)


```

The campaign looks like it started at __`r FirstDontRetire`__ with the last tagged tweet from the Aspen Institute coming at __`r LastDontRetire`__

```{r, fig.width=12, out.width="100%"}
tl_AspendIn %>% 
  unnest(cols = c(hashtags)) %>% 
  mutate(tweetDT = as.Date(created_at),
         DontRetire = str_detect(text, regex("#dontretirekid", ignore_case = TRUE)),
         tweetWK = lubridate::floor_date(tweetDT, "weeks")) %>% 
  count(tweetWK, DontRetire) %>% 
  ggplot(aes(tweetWK, n, color=DontRetire))+
    geom_point()+
    geom_line()+
    theme_bw()+
    labs(title = "Weekly Trend of #DontRetireKid Prevalence",
         x = NULL, y= "Count of Tweets")
```


Network graph of recent interactions with #dontretirekid

```{r, fig.width=12, out.width="100%"}
## search for #rstats tweets
drk <- search_tweets("#dontretirekid", n = 200)

## create from-to data frame representing retweet/mention/reply connections
drk_net_data <- network_data(drk, "retweet,mention,reply")

## if igraph is installed...
if (requireNamespace("igraph", quietly = TRUE)) {
  
  ## (1) convert directly to graph object representing semantic network
  drk_net <- network_graph(drk)
  
  ## (2) plot graph via igraph.plotting
  plot(drk_net)
}
```



Try to get the people who retweeted Aspen's tweets

```{r, echo=F, eval=F}
SampleID <- c("1237793396837810179")

get_retweeters(status_id = SampleID, n=10)


```



```{r, echo=F, eval=F}

exmpl <- tl_AspendIn %>% 
  filter(str_detect(text, "Please, coaches: ")) %>% 
  pull(status_id)


get_retweeters(status_id = exmpl, n=10)


```





```{r, eval=F}
data <- 
  unq_users %>%
  map(function(x) get_timeline(x, n = 1000)) %>%    # read in all the files individually
  reduce(rbind)  %>%       # reduce with rbind into one dataframe
  mutate(Year = lubridate::year(as.Date(created_at))) %>% 
  filter(Year == 2020,
         created_at >= FirstPrmt$MinDt) %>% 
  # filter(str_detect(text, regex("#dontretirekid", ignore_case = TRUE)))
  ungroup() %>% 
  select(status_id, reply_to_status_id, created_at, screen_name, reply_to_screen_name, mentions_screen_name,
         text, source, hashtags, urls_expanded_url, media_url,
         geo_coords, country, location,
         account_created_at, followers_count, friends_count)

```

## Gathering Participatation 




## Sport Participation

Not sure where we would gather the data from, but the goal would be to see if we could produce some level of causal inference test to see if the larger Project Play 


# Analysis

It might be interesting to do a sentiment analysis on the responses to the Don't Retire Kid tweets. 
```{r}

```



# Trends










